---
title: "Untitled"
output: html_document
date: "2024-05-14"
runtime: shiny
---

```{r echo=FALSE, message=FALSE}
library(shiny)
library(ggplot2)
library(dplyr)
library(readr)

current_ratio_tidy <- read.csv("current_ratio_tidy.csv")
return_on_assets_tidy <- read_csv("return_on_assets_tidy.csv")
debt_ratio_tidy <- read_csv("debt_ratio_tidy.csv")
all_headlines_tidy <- read_csv("all_headlines_tidy.csv")
```

### Current ratio

```{r echo=FALSE}
inputPanel(
  selectInput("sector", label = "Select Sector:", choices = c("All", unique(current_ratio_tidy$sector))),
  uiOutput("company_select")
)

renderPlot({
  filtered_data <- current_ratio_tidy
  
  if (input$sector != "All") {
    filtered_data <- filtered_data %>%
      filter(sector == input$sector)
  }
  
  if (!is.null(input$company)) {
    filtered_data <- filtered_data %>%
      filter(company %in% input$company)
  }
  
  filtered_data$year <- as.factor(filtered_data$year)
  
  ggplot(filtered_data, aes(x = year, y = debt_ratio, color = company)) +
    geom_line(aes(group = company)) +
    geom_point() +
    theme_minimal() +
    labs(
      x = "Year",
      y = "Debt Ratio",
      title = "Debt Ratio by Company Over Time",
      color = "Company"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
})

```

### Debt ratio

```{r echo=FALSE}
inputPanel(
  selectInput("sector2", label = "Select Sector:", choices = c("All", unique(debt_ratio_tidy$sector))),
  uiOutput("company_select2")
)

renderPlot({
  filtered_data <- debt_ratio_tidy
  
  if (input$sector2 != "All") {
    filtered_data <- filtered_data %>%
      filter(sector == input$sector2)
  }
  
  if (!is.null(input$company2)) {
    filtered_data <- filtered_data %>%
      filter(company %in% input$company2)
  }
  
  filtered_data$year <- as.factor(filtered_data$year)
  
  ggplot(filtered_data, aes(x = year, y = debt_ratio, color = company)) +
    geom_line(aes(group = company)) +
    geom_point() +
    theme_minimal() +
    labs(
      x = "Year",
      y = "Debt Ratio",
      title = "Debt Ratio by Company Over Time",
      color = "Company"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
})

```

### Return on Assets

```{r echo=FALSE}
inputPanel(
  selectInput("sector3", label = "Select Sector:", choices = c("All", unique(return_on_assets_tidy$sector))),
  uiOutput("company_select3")
)

renderPlot({
  filtered_data <- return_on_assets_tidy
  
  if (input$sector3 != "All") {
    filtered_data <- filtered_data %>%
      filter(sector == input$sector3)
  }
  
  if (!is.null(input$company3)) {
    filtered_data <- filtered_data %>%
      filter(company %in% input$company3)
  }
  
  filtered_data$year <- as.factor(filtered_data$year)
  
  ggplot(filtered_data, aes(x = year, y = debt_ratio, color = company)) +
    geom_line(aes(group = company)) +
    geom_point() +
    theme_minimal() +
    labs(
      x = "Year",
      y = "Debt Ratio",
      title = "Debt Ratio by Company Over Time",
      color = "Company"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
})

```

### Companies headquarters

```{r}
companies_hq <- read_csv("companies_hq.csv")

library(leaflet)

leaflet(companies_hq) %>%
  addTiles() %>%
  addCircleMarkers(
    data = companies_hq,
    lat = ~latitude,
    lng = ~longitude,
    radius = ~sqrt(revenue) / 100, #resize
    fillColor = "blue",
    fillOpacity = 0.4,
    popup = ~paste0("<b>Company:</b> ", company, "<br>",
                    "<b>Address:</b> ", address, "<br>",
                    "<b>Revenue:</b> $", format(revenue, big.mark = ","))
  )
```

### Sentimental analysis

```{r}
sentiment_by_company <- all_headlines_tidy %>%
  group_by(company, year) %>%
  summarise(avg_sentiment = mean(value),
            sd_sentiment = sd(value)/ sqrt(length(value)))#using standard erro

print(sum(is.na(sentiment_by_company$avg_sentiment)))

ggplot(sentiment_by_company, aes(x = company, y = avg_sentiment, fill = avg_sentiment)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = avg_sentiment - sd_sentiment, ymax = avg_sentiment + sd_sentiment), width = 0.2) +
  scale_fill_gradient(low = "gray", high = "orange") +
  theme_minimal() +
  ggtitle("Average Sentiment Trends by Company") +
  xlab("Company") +
  ylab("Average Sentiment")+
  coord_flip()

filtered_data <- all_headlines_tidy %>%
    filter(company == "disney", year == 2015)
  
  # Count word occurrences
  top_words <- filtered_data %>%
    group_by(word) %>%
    summarise(
      occurrences = n(),
      avg_value = mean(value)
    ) %>%
    arrange(desc(occurrences)) %>%
    slice_head(n = 5)
  
  ggplot(top_words, aes(x = reorder(word, occurrences), y = avg_value, fill = avg_value)) +
    geom_bar(stat = "identity") +
    #geom_shadowtext(aes(label = word), colour = "black", hjust = 0, nudge_x = 0.3) +
    geom_text(aes(label = word),position = position_stack(vjust= 0.5), colour = "white") + 
    theme_minimal()  +
    theme(axis.text.y = element_blank()) +
    scale_fill_gradient2(low = "#0C7BDC", mid = "gray", high = "#FFC20A", midpoint = 0) +
    ggtitle("Top 5 Words by Company and Year") +
    xlab("Word") +
    ylab("Average Value") +
    coord_flip()
```


## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



