---
title: "Untitled"
output: html_document
date: "2024-05-14"
runtime: shiny
---

```{r}
current_ratio_tidy <- read_csv("current_ratio_tidy.csv")

current_ratio_tidy$year <- as.factor(current_ratio_tidy$year)

ggplot(current_ratio_tidy, aes(x = year, y = debt_ratio, color = company)) +
  geom_line(aes(group = company)) +
  geom_point() +
  theme_minimal() +
  labs(
    x = "Year",
    y = "Debt Ratio",
    title = "Debt Ratio by Company Over Time",
    color = "Company"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
debt_ratio_tidy <- read_csv("debt_ratio_tidy.csv")

debt_ratio_tidy$year <- as.factor(debt_ratio_tidy$year)

ggplot(debt_ratio_tidy, aes(x = year, y = debt_ratio, color = company)) +
  geom_line(aes(group = company)) +
  geom_point() +
  theme_minimal() +
  labs(
    x = "Year",
    y = "Debt Ratio",
    title = "Debt Ratio by Company Over Time",
    color = "Company"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
```{r}
return_on_assets_tidy <- read_csv("return_on_assets_tidy.csv")

return_on_assets_tidy$year <- as.factor(return_on_assets_tidy$year)

ggplot(return_on_assets_tidy, aes(x = year, y = debt_ratio, color = company)) +
  geom_line(aes(group = company)) +
  geom_point() +
  theme_minimal() +
  labs(
    x = "Year",
    y = "Debt Ratio",
    title = "Debt Ratio by Company Over Time",
    color = "Company"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



